Parallel Deduplication with Batch Scheduling for Collocated Virtual Machine Backup in the Cloud

### 2014-01-15 batchdedup/analysis.tex

>>>>

\subsection{Metrics}
We have chosen two primary metrics to evaluate our approach and the efficiency
of our scheduling (discussed in the next section). The first metric is total
jobspan. This metric is used to determine how long of a backup window is
required for each round of backups, and also can show throughput of the entire
system.

Our system uses a multi-round batch approach, so we need another metric to
evaluate how the rounds affect time.  The second metric we have chosen is
average VM backup time. This metric helps us to compare different schedules,
and evaluate the tradeoff between batch efficiency and the time that VMs are
spent in backup (which affects CoW). Within a round, we assign all VMs the backup time
for that round, and then compute the mean backup time across all VMs.
